---
title: '4-RR-WordProblems-Geography'
author: "Anoff Nicholas Cobblah"
date: "December 16, 2017"
output:
  html_document:
    number_sections: yes
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Geography in 19th Century Word Problems

This is the most ambitious of the word problem searches, as there are so many possibilities that the searched term list had to be broken into multiple vectors.


```{r word term region}

regionterm <- c("americas","north america","south america","central america","asia","orient","crimea","mediterranean","baltic","africa","colonies","atlantic","pacific","east","west","north","south","arctic","europe")
nationalityterm <- c("afghan", "algerian", "american", "argentinian", "australian", "austrian", "bahaman", "belgian", "bohemian","bolivian","brazilian","british","bulgarian","californian","canadian","chilean","chinese","confederate","costa rican","cuban","egyptian","english","ethiope","ethiopian","fijian","floridian","frank","french","german","greek","guatemalan","hatian","hawaiin","hungarian","indian","irish","italian","japanese","korean","liberian","mexican","moroccan","peruvian","portuguese","prussian","roman","romanian","russian","scottish","sicilian","south african","spanish","sudanese","swedish","swiss","tahitian","tunesian","tuscan","venezuelan","welsh","yankee")
nationterm1 <- c("aceh","acre","afghanistan","ahom","ajaigarh","algarves","algeria","alipura","alirajpur","alsace-lorraine","alwar","andorra","angoche","angola","anhalt","anhalt-bernburg","anhalt-dessau","anhalt-k?then","ankole","annam","antigua","anziku","araucan?a","argentina","argentine","aro confederacy","aschaffenburg","ashanti","athgarh","aussa","australia","austria","austria-hungary","austrian","baden","baguirmi","bahamas","bamana","banten","baol","barbados","barotseland","basutoland","batavian","bat?","bavaria","bechuanaland","beihan","belgium","benin","berg","bhutan","bhutan","bohemia","bolivia","bora bora","bornu","bourbon","bourbon spain","brazil","bremen","bruneian","brunswick","brunswick-l?neburg","buganda","bukhara","bulgaria","bundu","bunyoro","burma","burundi","california","cambodia","canada","cape colony","cape verde","carrara","cayor","central america","ceylon","chad","champa","champasak","chan santa cruz","cherokee nation","chile","china","cisalpine","cochin","cochinchina","colombia","comoros","confederate states","congo","cook islands","cospaia","costa rica","croatia","croatia-slavonia","cuba","dahomey","damagaram","darfur","dendi","denmark","denmark-norway","dhala","diriyah","dominica","dominican","durrani","dutch cape colony","east indies","easter island","ecuador","egypt","el salvador","elba","england","ethiopia","etruria","ezo","fante","fiji","finland","first hellenic","formosa","france","frankfurt","french","futa jallon","futa toro","galicia","gambia","garhwal","garo","gaza","genoa","german","german south-west africa","germany","gilbert and ellice islands","gomma","governorate of estonia","gozo","gran colombia","granadine","great britain","greece","guatemala","guiana","guinea","gumma","gyaaman","habsburg monarchy","haiti","hamburg","hanover","hawaii","helvetic","hesse","hesse-darmstadt","hesse-homburg","hobyo","hohenzollern-hechingen","hohenzollern-sigmaringen","holland","holstein","holy roman","honduras","huahine","hungary","huraa dynasty","hyderabad","illyrian provinces","imereti","india","ionian islands","ireland","italian","italy","jabal shammar","jaisalme","jammu","janjero","japan","jimma","johor","jolof","joseon","kaabu","kaarta","kaffa","kamerun","kano","kasanje","kashmir","kazakh khanate","kazembe","k?n?dougou","kharan","khasso","khiva","kokand","konbaung dynasty","kong","kongo","korea","kosovo vilayet","koya","krak?w","kuba","kuwait","lanfang","las bela","leyen","liberia","liechtenstein","liga federal","ligurian","limmu-ennarea","lippe","loango","lodomeria","lombardy-venetia","luba","l?beck","lucca","lunda","luxembourg","maguindanao","mainz","majeerteen","makran","malay","malta","mangareva","manipur","manitoba","maratha","maravi","maryland","massa","massina","mecklenburg-schwerin","mecklenburg-strelitz","medri bahri","merina","mexican","mexico","modena","moldavia","moldavia","monaco","montenegro","morocco","mosquito coast","mossis","mozambique","mthethwa paramountcy","mthwakazi","mughal","muscat","muskogee","mysore","naples","nassau","natal","nejd","nepal","netherlands","new granada","new guinea","new zealand ","nguyen dynasty","nicaragua","nieuwe republiek","niue","niuean monarchy","north borneo","north german","norway","nri","oldenburg","oman","orange","orungu","ottoman","ouaddai","oyo","pahang","papal states","papua","paraguay","parma","pashalik of timbuktu","patagonia","pattani","perak","persia","peru","peru-bolivian","portugal","pr?ncipe","prussia","qing dynasty","ragusa","raiatea","rarotonga","regensburg","reggio","reuss","reuss-ebersdorf","reuss-gera","reuss-greiz","reuss-lobenstein","rhodesia","roman","romania","roquebrune-cap-martin","rozwi","russian","rwanda","ryukyu","sahara","saint lucia","saint vincent and the grenadines","saint-domingue","samao","samoa","san marino","s?o tom?","sarawak","sardinia","saxe-altenburg","saxe-coburg and gotha","saxe-coburg-saalfeld","saxe-gotha-altenburg","saxe-hildburghausen","saxe-lauenburg","saxe-meiningen","saxe-weimar-eisenach","saxony","schaumburg-lippe","schleswig","schwarzburg-rudolstadt","schwarzburg-sondershausen","scotland","sedang")
nationterm2 <- c("selangor","sennar","septinsular","serbia","shilluk","siam","sicily","sierra leone","sikh","sikkim","sine","sirmoor","sokoto caliphate","solomon islands","somaliland","sonora","soran","south africa","spain","straits","sudan","sulu","surinam","swaziland","sweden","swiss","switzerland","tahiti","texas","the maldives","the netherlands","the rhine","the r?o de la plata","the rio grande","the river plate","the two sicilies","timor","tobago","togoland","tokugawa","tonga","tonkin","toucouleur","transvaal colony","travancore","tridentum","trinidad","trucial","tuscany","united states","upper aulaqi","upper yafa","uruguay","venezuela","wadai","wahidi balhaf","wahidi haban","waldeck","wales","wallachia","warsangali","warsaw","wassoulou","welayta","west africa","west florida","westphalia","wituland","w?rttemberg","w?rzburg","yeke","yucat?n","zanzibar","zulu")
```

Again, we start working with the actual data once our terms are set, and don't bother with categories.

```{r word problem nation term frequencies, eval=FALSE}
    WPKWIC <- read.delim(paste0(getwd(),"/","Word-Problems-Data/","wordproblemsKWIC.txt"), header = FALSE, sep="\t")
    stemregionterm <- unique(wordStem(regionterm))
    stemnationalityterm <- unique(wordStem(nationalityterm))
    stemnationterm1 <- unique(wordStem(nationterm1))
    stemnnationterm2 <- unique(wordStem(nationterm2))
    stemsearchedterms <- c(stemregionterm,stemnationalityterm,stemnationterm1,stemnnationterm2)

    lemma <- list()
    data <- matrix(,ncol=5,nrow=1)
    colnames(data) <- c("Word_Problem_ID","stemsearchedterm","Lemma","Category","Word_Problem")
      for (p in 1:length(stemsearchedterms)) {
        iterp <- 1
        tempdata <- matrix(,ncol=5,nrow=1) #this matrix is supposed to get wiped every loop.
        for (i in 1:nrow(WPKWIC)) {
          ltoken <- tokenize_words(as.vector(WPKWIC[i,]), lowercase = TRUE, stopwords = NULL, simplify = FALSE)
          ltoken <- unlist(ltoken)
          stemltoken <- wordStem(ltoken)
          for (w in 1:length(ltoken)) {
            if(stemltoken[w] == stemsearchedterms[p]) {
              lemma[[iterp]] <- w
              iterp <- iterp+1
            }
          }
          lemma <- unlist(lemma)
          #Now it's time to start adding what we've found for this document into our data matrix.
            mat <- matrix(,ncol=5,nrow=length(lemma)) #for documents with no matches, mat will have no rows, which is perfect.
            mat[,1] <- i
            mat[,2] <- stemsearchedterms[p]
            mat[,3] <- lemma
            mat[,4] <- NA
            mat[,5] <- as.character(WPKWIC[i,])
            tempdata <- rbind(tempdata,mat)
            lemma <- list()
            lemma_perc <- list()
        }
          tempdata <- tempdata[-1,]
          data <- rbind(data,tempdata)
      }
    WPnationdata <- data[-1,]
    WPWPnationdatadf <- as.data.frame(WPnationdata)
    WPWPnationdatadf$Word_Problem <- as.character(WPWPnationdatadf$Word_Problem) #need this column to be a character column for below
    WPWPnationdatadf$Word_Problem_ID <- as.character(WPWPnationdatadf$Word_Problem_ID) #need this column to be a character column for below
    WPWPnationdatadf
```

As usual, you might want to save this data. You can do so using the script below.

```{r save word problem nation, eval=FALSE}
    tempname <- paste0(getwd(),"/","Word-Problems-Data/","WPdata-nation.txt")
    write.table(WPWPnationdatadf, file=tempname)
```

And we can quickly visualize the counts by using ggplot. France is far and away the winner. A little thought reveals that "acr" is a false datapoint, referring not the the nation but to the unit of measure.

```{r word problem nation visualize, eval=FALSE}
    p <- ggplot(WPWPnationdatadf, mapping = aes(x = stemsearchedterm))
      pg <- geom_bar()
      pl <- p + pg + labs(x = "Nation", title =  "Racial Terms in Word Problems") +coord_flip()
      print(pl)
```

